---
title: "Baseline Monitoring Report"
author: "Water Action Volunteers"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
params:
  year: NA
  stn: NA
  data: NA
---

```{r setup, include=FALSE}
stn <- params$stn


```


# Water Action Volunteers

Station name: `r stn$station_name`
Station ID: `r stn$station_id`
Location: `r stn$latitude`, `r stn$longitude`
County: `r stn$county_name` County
Region: `r stn$dnr_region`
Waterbody: `r stn$waterbody`
WBIC: `r stn$wbic`
Subwatershed: `r stn$sub_watershed` (`r stn$huc12`)
Watershed: `r stn$watershed` (`r stn$huc10`)
Subbasin: `r stn$sub_basin` (`r stn$huc8`)
Basin: `r stn$major_basin`


## Baseline data summary

```{r}
df <- params$data$baseline %>%
  filter(station_id == stn$station_id)

options(knitr.kable.NA = "-")

df %>%
  select(
    `Date` = date,
    `Fieldwork #` = fieldwork_seq_no,
    `Air temp (°C)` = ambient_air_temp,
    `Water temp (°)` = water_temp,
    `Dissolved oxygen (mg/L)` = d_o,
    `DO % saturation` = d_o_percent_saturation,
    `pH` = ph,
    `Transparency (cm)` = transparency_average,
    `Stream width (ft)` = stream_width,
    `Average depth (ft)` = average_stream_depth,
    `Surface velocity (ft/s)` = average_surface_velocity,
    `Streamflow (cfs)` = streamflow_cfs,
    `Weather` = weather_last_2_days
  ) %>% knitr::kable()
```


## Water Temperature

