---
date: "Downloaded on `r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
fontsize: 11pt
geometry: left=0.75in, right = 0.75in, top=0.75in, bottom=0.75in
header-includes:
  \usepackage{colortbl}
  \usepackage{booktabs}
  \usepackage{tabu}
  \usepackage{longtable}
  \usepackage{enumitem}
  \renewcommand{\familydefault}{\sfdefault}
params:
  year: NA
  stn: NA
  data: NA
title: "`r params$stn$label`"
author: "`r params$year` Fieldwork Report"
---

```{r setup, include = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = "-")
options(scipen = 999)
stn <- params$stn
baseline <- params$data$baseline %>%
  mutate(formatted_date = format(date, "%b %d"))
```

# Water Action Volunteers

Station name: `r stn$station_name`\
Station ID: `r stn$station_id`\
Location: `r stn$latitude`, `r stn$longitude`\
County: `r stn$county_name` County\
Region: `r stn$dnr_region`\
Waterbody: `r stn$waterbody`\
WBIC: `r stn$wbic`\
Subwatershed: `r stn$sub_watershed` (HUC12: `r stn$huc12`)\
Watershed: `r stn$watershed` (HUC10: `r stn$huc10`)\
Subbasin: `r stn$sub_basin` (HUC08: `r stn$huc8`)\
Basin: `r stn$major_basin`

## Baseline data summary

```{r}
baseline %>%
  select(
    `Date` = formatted_date,
    # `Fieldwork #` = fieldwork_seq_no,
    `Air temp (°C)` = ambient_air_temp,
    `Water temp (°)` = water_temp,
    `Dissolved oxygen (mg/L)` = d_o,
    `DO % sat.` = d_o_percent_saturation,
    `pH` = ph,
    `Transparency (cm)` = transparency_average,
    `Weather` = weather_last_2_days
  ) %>% kable()
```


## Streamflow summary

```{r}
baseline %>%
  select(
    `Date` = formatted_date,
    # `Fieldwork #` = fieldwork_seq_no,
    `Stream width (ft)` = stream_width,
    `Average depth (ft)` = average_stream_depth,
    `Surface velocity (ft/s)` = average_surface_velocity,
    `Streamflow (cfs)` = streamflow_cfs
  ) %>% kable()
```

## Water Temperature

